Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-13 manuscript/manuscript.tex
Minor improvements in manuscript

Because the grid search was limited to specific values of $b$ and used only one grid, we
will determine the optimal value of $\delta$ for exponential density tesseroids on the
next subsection.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-density-diffs.pdf}
\caption{
    Numerical error for different exponential density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by a spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-exp}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the 20 shell models detailed on Table~\ref{tab:tess-collections} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case ($D = 1, 2.5$ for the potential and $g_z$, respectively).
    The difference is reported as a percentage of the shell values.
    To improve visualization of the results, each curve corresponds to the maximum
    difference between every shell model.
    }
\label{fig:delta-exponential}
\end{figure*}

>>>>

Because the grid search was limited to specific values of $b$ and used only one grid, we
will perform a more detailed analysis for $\delta$ determination in case of exponential
density tesseroids.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-density-diffs.pdf}
\caption{
    Numerical error for different exponential density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by a spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-exp}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the 20 shell models detailed on Table~\ref{tab:tess-collections} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case.
    The difference is reported as a percentage of the shell values.
    Each curve corresponds to the maximum difference between every shell model.
    }
\label{fig:delta-exponential}
\end{figure*}
